---
title: "carabids_EDA"
author: "Anna Spiers"
date: "1/28/2020"
output: rmarkdown::github_document
---

```{r, results=FALSE}
library(neonUtilities)
```

##### Carabid data
```{r}
carabids_all <- loadByProduct(dpID = "DP1.10022.001", site = "NIWO") #ground beetles
#list2env(carabids_all, .GlobalEnv) splits 
save as rdata

```


To Do
which df's from the carabid dataset are important?
find relevant Niwot data
find relevant Ameriflux data

##### Predictor variable NEON dpIDs
DP3.30025.001 slope/aspect 
DP3.30024.001 elevation - hydrology (DEM)
DP1.00006.001 precipitation
DP1.00098.001 relative humidity
DP1.00005.001 IR biological temp
DP1.00014.001 Shortwave radiation (direct and diffuse pyranometer)
DP1.00023.001 Shortwave and longwave radiation (net radiometer)
DP2.30012.001 LAI - spectrometer - flightline
DP1.00041.001 soil temp
DP1.00094.001 Soil water content and water salinity
DP1.00041.001 soil temp
DP1.10098.001 Woody plant vegetation structure
DP1.10033.001 Litterfall and fine woody debris sampling

microtopography
canopy gaps
canopy cover
